Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-04-07 paper.tex
Alice doesn't like that paragraph

The paper is organised as follows: we present the 13 match racing rules and then the constraint
models and four stages of schedule construction, schedules are then presented, there is then a
discuss and we conclude.

>>>>

The paper is organised as follows: we introduce the 13 match racing rules, then explain the
constraint models and four stages of schedule construction, and then schedules are presented. We
finish with discussion and a conclusion.
